Evaluation of the George Year 2 System

### 2011-03-31 code/subarchitectures/vision.sa/branches/post-review-yr2-11533/src/c++/vision/components/VisualLearner/test/gy2report/gy2article.tex
title, figure size
george tester parameters

@@

\begin{figure}
\includegraphics[width=0.8\textwidth]{xdata/simple_states.pdf}
\label{fig:simpleStates}
\caption{Basic state machine for the automated tutor}
\end{figure}

@@

Although the previous learning task has been completed, the change in the
contents of the set of VisualObjects in the WM locks the planner as in the
previous case.

@@

>>>>

\title{Evaluation of the George Year 2 System}
\author{Marko Mahnič\\ University of Ljubljana}
\date{2011-03-16}

\maketitle

@@

\begin{figure}
\includegraphics[width=0.6\textwidth]{xdata/simple_states.pdf}
\label{fig:simpleStates}
\caption{Basic state machine for the automated tutor}
\end{figure}

@@

The change in the contents of the set of VisualObjects in the WM locks the
planner again: when a teaching goal for the new object appears, the planner
creates a plan that includes a belief about an object that has just
disappeared. This results in a plan in a {\tt PENDING} state.

@@

On rare occasions Matlab VisualRecognizer crashes when rendering the
recognition results.
